### 2018-03-17 paper/5-implementations.tex

\begin{enumerate}
\item Any system using verifying traces, e.g. \Shake, is unlikely to see significant benefit from storing more than one \hs{Trace} per key\footnote{There is a small chance of a benefit if the dependencies change but the result does not, and then the dependencies change back to what they were before.}. Therefore, such systems can store \hs{Map}~\hs{k}~\hs{(Trace}~\hs{k}~\hs{v)}, where the initial \hs{k} is the \hs{key} field of \hs{Trace}.
\item Any system using \hs{Applicative} dependencies can omit the dependency keys from the \hs{Trace} as they can be recovered from the \hs{key} field.
\item Any \hs{Applicative} build system storing constructive traces, e.g. \Bazel, can index directly from the key and results to the output result~--~i.e. \hs{Map}~\hs{(@@k,}~\hs{[Hash}~\hs{v])}~\hs{(Hash}~\hs{v)}. Importantly, assuming the traces are stored on a central server, the client can compute the key and the hashes of its dependencies, then make a single call to the server to retrieve the result hash. In this formulation we have removed the possibility for a single key/dependency state to map to multiple different hashes, e.g. on a non-deterministic build~--~something \Bazel already prohibits which is discussed more in~\S\ref{sec-non-determinism}.
\item Finally, a \hs{Monad} build system with constructive traces can be represented as \hs{Map}~\hs{k}~\hs{(Choice}~\hs{k}~\hs{v)}, assuming a definition of \hs{Choice} as:
\begin{minted}[xleftmargin=10pt]{haskell}
data Choice k v = Choice k (Map (Hash v) Choice)
                | Result (Hash v)
\end{minted}
Here the \hs{Choice} encodes a tree, asking successive questions about keys, and taking different branches based on the answers, until it reaches a final result. Implementing this structure over client-server communication requires either a chatty interface with lots of round-trips per \hs{Choice} step, or sending over a part of the tree that is not subsequently explored.
\end{enumerate}

>>>>

\begin{enumerate}
\item Any system using verifying traces, e.g. \Shake, is unlikely to see significant benefit from storing more than one \hs{Trace} per key\footnote{There is a small chance of a benefit if the dependencies change but the result does not, and then the dependencies change back to what they were before.}. Therefore, such systems can store \hs{Map}~\hs{k}~\hs{(Trace}~\hs{k}~\hs{v)}, where the initial \hs{k} is the \hs{key} field of \hs{Trace}.
\item Any system using \hs{Applicative} dependencies can omit the dependency keys from the \hs{Trace} as they can be recovered from the \hs{key} field.
\item Any \hs{Applicative} build system storing constructive traces, e.g. \Bazel, can index directly from the key and results to the output result~--~i.e. \hs{Map}~\hs{(@@k,}~\hs{[Hash}~\hs{v])}~\hs{(Hash}~\hs{v)}. Importantly, assuming the traces are stored on a central server, the client can compute the key and the hashes of its dependencies, then make a single call to the server to retrieve the result hash. In this formulation we have removed the possibility for a single key/dependency state to map to multiple different hashes, e.g. on a non-deterministic build~--~something \Bazel already prohibits which is discussed more in~\S\ref{sec-non-determinism}.
\item Finally, a \hs{Monad} build system with constructive traces can be stored as \hs{Map}~\hs{k}~\hs{(Choice}~\hs{k}~\hs{v)}, assuming a definition of \hs{Choice} as:
\begin{minted}[xleftmargin=10pt]{haskell}
data Choice k v = Choice k (Map (Hash v) Choice)
                | Result (Hash v)
\end{minted}
Here the \hs{Choice} encodes a tree, asking successive questions about keys, and taking different branches based on the answers, until it reaches a final result. Implementing this structure over client-server communication requires either a chatty interface with lots of round-trips per \hs{Choice} step, or sending over a part of the tree that is not subsequently explored.
\end{enumerate}
